INTELLIGENT SYSTEMS

### 2021-04-19 papers/paper_10.tex
finish 10.2.4

\subsubsection{RUSBoost Methodology}
The RUSBoost algorithm has the task of identifying each dolphin and predicting 
its label. The application of this algorithm can be schematized in 
figure \ref{fig:RUSBoost}. The architecture consists of 3 main phases:
\begin{enumerate}
    \item \emph{Pre-processing}: creation of the black and white image containing the 
    extracted fin.
    \item \emph{Features Extraction}: build the 3-dimensional super-SIFT descriptor. 
    \item \emph{Classification}: application of the RUSBoost algorithm.
\end{enumerate}
RUSBoost consists of two other types of algorithms: Random Under-Sampling 
(RUS) and Adaboost \cite{0907875811}. RUSBoost training takes place by carrying out 
cross-validation, one-vs-all, on a set of labeled data of the 23 dolphins considered.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper10/RUSBoost.png}
    \centering
    \caption{Experimental methodology based on RUSBoost.}
    \label{fig:RUSBoost}
\end{figure}

\subsubsection{RUSPool}

>>>>

\subsubsection{RUSBoost Methodology}
The RUSBoost algorithm has the task of identifying each dolphin and predicting 
its label. The application of this algorithm can be schematized in 
figure \ref{fig:RUSBoost}. The architecture consists of 3 main phases:
\begin{enumerate}
    \item \emph{Pre-processing}: creation of the black and white image containing the 
    extracted fin.
    \item \emph{Features Extraction}: build the 3-dimensional super-SIFT descriptor. 
    \item \emph{Classification}: application of the RUSBoost algorithm.
\end{enumerate}
RUSBoost consists of two other types of algorithms: Random Under-Sampling 
(RUS) and Adaboost \cite{0907875811}. RUSBoost training takes place by carrying out 
cross-validation, one against all, on each of the 23 dolphins taken into consideration, 
therefore $M_i$ classifiers will be created, with $i = 1,2,...,23$.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper10/RUSBoost.png}
    \centering
    \caption{Experimental methodology based on RUSBoost.}
    \label{fig:RUSBoost}
\end{figure}

\subsubsection{RUSPool}
The RUSPool algorithm aims to identify known dolphins among all and unknown 
ones. This task is done by using the previous 23 already trained 
RUSBoosts classifiers (Fig. \ref{fig:RUSPool Arch}). Therefore, each image given as input to RUSPool 
will have n super-SIFT descriptors associated with it and this new sample is 
supplied as input to the RUSBoosts classifiers. The result returned by each 
classifier will represent the prediction that a dolphin has been recognized or 
not. The result obtained from the difference in these probabilities, if greater 
than a threshold equal to $0.11$, will be taken into consideration, discarding 
all other cases of uncertainty. The final output will be a vector $R$ where its 
elements $r_i$ represent the percentage of positive predictions for each classifier 
$M_i$ (Fig. \ref{fig:ri}). A filter is applied on the vector R to obtain the 
prediction of the identity of a dolphin given in input.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.5\linewidth]{images/paper10/RUSPool Architecture.png}
    \centering
    \caption{RUSPool Architecture.}
    \label{fig:RUSPool Arch}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.4\linewidth]{images/paper10/ri.png}
    \centering
    \caption{Example of RUSPool output. $r_i$ is the bumber of positive predicitons of the $M_i$ classifiers.}
    \label{fig:ri}
\end{figure}

\subsubsection{Convolutional Neural Network}
A convolutional neural network (CNN) is used. Its architecture is composed 
of a triple sequence of Conv-ReLu-MaxPool layers (Fig. \ref{CNNDol}). The number of 
parameters and images useful for training the network is less than the most 
widespread neural networks in the state of the art, thus reducing the problem 
of overfitting. This architecture forms the previous NNPool network. The 
dataset used is the one previously mentioned DNN.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper10/NNPool Architecture.png}
    \centering
    \caption{CNN Architecture build for each dolphin.}
    \label{fig:CNNDol}
\end{figure}

\subsubsection{NNPool}
